---
title: "Parâmetros"
output: html_document

params:
  symbol1: "^BVSP"
  symbol2: ""
  
  periodicit:
    label : "periodicity"
    input: select
    value : "daily"
    choices : ["daily", "weekly", "monthly"]
    
  years:
    label: "Year0"
    value: 2017
    input: slider
    min: 2000
    max: 2020
    step: 1
    sep: ""
    
  months:
    label: "Month 0"
    input: slider
    value: 1
    min: 1
    max: 12
    step: 1
    sep: ""
    
---

# Introduction

```{r include = FALSE}
library(quantmod)
library(dygraphs)
library(shiny)

s=(paste(params$years,"-",params$months,"-01"))
s=gsub(" ","",s)

stock1 <- getSymbols.yahoo(params$symbol1, auto.assign = FALSE, from = s,
                    end=Sys.Date(),periodicity=params$periodicit)
stock2 <- getSymbols.yahoo(params$symbol2, auto.assign = FALSE,from = s,
                     end=Sys.Date(),periodicity=params$periodicit)

```


This report examines the price of two stocks: 
  
* ``r params$symbol1``
* ``r params$symbol2``

It is written in [R Markdown](http://rmarkdown.rstudio.com), an authoring format that enables easy creation of dynamic documents, presentations, and reports from R. R Markdown combines the core syntax of **markdown** (an easy to write plain text format) with embedded **R** code chunks that are run so their output can be included in the final document.

The data comes from [Yahoo finance](http://finance.yahoo.com).

### ``r params$symbol2`` price

```{r, echo = FALSE}
dygraph(cbind(Cl(stock2),Op(stock2)))
```

### ``r params$symbol2`` oscilation(%)
```{r echo = FALSE,cache=TRUE}
dygraph(cbind(100*(Cl(stock2)/Op(stock2)-1),
      100*(Cl(stock1)/Op(stock1)-1)))

```

### ``r params$symbol2`` acumalitve(%)

```{r echo = FALSE}

o1 <- as.numeric(Op(stock1)[1][1])

s1 <- Cl(stock1)/o1-1

o2 <- as.numeric(Op(stock2)[1][1])
s2 <- Cl(stock2)/o2-1

dygraph(cbind(100*s2, 100*s1))
```
